Verifying Demonstrations

### 2018-02-28 paper/TimeStamp.tex

We can instantiate \(\TS\) using a blockchain.
The \(\TSstamp[x]\) algorithm will simply include \(x\) in the blockchain.
\(\TSget\) will return the hash of the current head of the chain.
This value is difficult to predict since it depends on all submitted 
transactions.
This forces us to make the assumption that the adversary cannot control 
\emph{all} transactions that are submitted to the blockchain.
As long as one non-adversarial transaction is submitted it will be 
unpredictable.
The blockchain must also be continuously extended, \eg as in
Bitcoin~\cite{Bitcoin}, where a new block appears approximately every 10 
minutes.
This coarse-grained form of time-stamping is enough for our purposes.

There are some additional properties that we need from \(\TS\).
First, we need immutability, \ie once we commit something (through \(\TSstamp\)) 
it will remain there.
This is usually true for blockchains.
We will use this to ensure verifiability, the data must remain to be verifiable.

>>>>

We can instantiate \(\TS\) using a blockchain, \eg OmniLedger~\cite{OmniLedger}.
The \(\TSstamp[x]\) algorithm will simply include \(x\) in the blockchain and 
return the block into which \(x\) was included.
\(\TSget\) will return the hash of the current head of the chain.
This value is difficult to predict since it depends on all submitted 
transactions and usually some randomness, \eg nonces and miners' secrets.
The blockchain must also be continuously extended, \eg as in
Bitcoin~\cite{Bitcoin}, where a new block appears approximately every 10 
minutes.
So having a dedicated blockchain for a protest will not do, it is better to use 
a blockchain which is also used for other things too.

There are some additional properties that we need from \(\TS\), which are 
implied by blockchains.
First, we need immutability, \ie once we commit something (through \(\TSstamp\)) 
it will remain there.
We will use this to ensure verifiability, the data must remain to be verifiable.
